\documentclass[TOTEM]{cern/cernphprep}

\def\d{{\rm d}}
\def\un#1{\,{\rm #1}}
\def\ung#1{\quad[{\rm #1}]}
\def\unt#1{[{\rm #1}]}
\def\e{{\rm e}}

\setbox123\hbox{\small$0$}
\def\S{\hbox to\wd123{\hss}}
\setbox124\hbox{\small$_{0}$}
\def\s{\hbox to\wd124{\hss}}

\def\etal{et al.}
\def\acknowledgments{\section*{Acknowledgements}}
\def\Name#1{\textsc{#1}, }
\def\REVIEW#1#2#3#4{{\it #1} {\bf #2} (#3) #4}

\def\Instline#1#2{%
	\expandafter\write1{\string\newlabel{#1}{{#1}{}}}%
	\hbox to\hsize{\strut\hss$^{#1}$#2\hss}
}

\def\hang{\hangindent=\parindent}
\catcode`\>=11
\newskip\itskip \itskip2mm
\newskip\iitskip \iitskip0mm
\newdimen\itindent \itindent3mm
\newdimen\iitindent \iitindent5mm
\def\>{\par\vskip\itskip\parindent\itindent\indent\hang\llap{\hbox to3mm{$\bullet$\hss}}}
\def\>E{\par\vskip\itskip\parindent\itindent\indent\hang\llap{\hbox to3mm{\hss}}}
\def\>>{\par\vskip\iitskip\parindent\iitindent\indent\hang\llap{\hbox to\iitindent{\hss--\ }}}



%----------------------------------------------------------------------------------------------------

\begin{document}

\begin{titlepage}

\renewcommand{\EXPLOGO}{fig/logo_totem_black.pdf}

\PHnumber{XXXX}
\PHdate{XXXX}

\EXPnumber{XXXX}
\EXPdate{XXXX}

\title{Measurement of Elastic pp Scattering at $\sqrt{\hbox{s}} = \hbox{8}$\,TeV in the 
Coulomb-Nuclear Interference Region by the TOTEM Experiment at the CERN LHC}

\ShortTitle{Meas.~of Elastic pp Scattering at $\sqrt{\hbox{s}} = \hbox{8}$\,TeV in the 
CNI Region by TOTEM}

\Collaboration{The TOTEM Collaboration}
\ShortAuthor{The TOTEM Collaboration (G.~Antchev \emph{\etal})}

\iffalse
\begin{Authlist}
G.~Antchev\Aref{a},
P.~Aspell\Iref{8},
I.~Atanassov\IAref{8}{a},
V.~Avati\Iref{8},
J.~Baechler\Iref{8},
V.~Berardi\IIref{5b}{5a},
M.~Berretti\Iref{7b},
E.~Bossini\Iref{7b},
M.~Bozzo\IIref{6b}{6a},
P.~Brogi\Iref{7b},
E.~Br\"{u}cken\IIref{3a}{3b},
A.~Buzzo\Iref{6a},
F.~S.~Cafagna\Iref{5a},
M.~Calicchio\IIref{5b}{5a},
M.~G.~Catanesi\Iref{5a},
C.~Covault\Iref{9},
M.~Csan\'{a}d\IAref{4}{e},
T.~Cs\"{o}rg\H{o}\Iref{4},
M.~Deile\Iref{8},
K.~Eggert\Iref{9},
V.~Eremin\Aref{b},
R.~Ferretti\IIref{6a}{6b},
F.~Ferro\Iref{6a},
A. Fiergolski\Aref{c},
F.~Garcia\Iref{3a},
S.~Giani\Iref{8},
V.~Greco\IIref{7b}{8},
L.~Grzanka\IAref{8}{d},
J.~Heino\Iref{3a},
T.~Hilden\IIref{3a}{3b},
R.~A.~Intonti\Iref{5a},
J.~Ka\v{s}par\IIref{1a}{8},
J.~Kopal\IIref{1a}{8},
V.~Kundr\'{a}t\Iref{1a},
K.~Kurvinen\Iref{3a},
S.~Lami\Iref{7a},
G.~Latino\Iref{7b},
R.~Lauhakangas\Iref{3a},
T.~Leszko\Aref{c},
E.~Lippmaa\Iref{2},
M.~Lokaj\'{\i}\v{c}ek\Iref{1a},
M.~Lo~Vetere\IIref{6b}{6a},
F.~Lucas~Rodr\'{i}guez\Iref{8},
M.~Macr\'{\i}\Iref{6a},
T.~M\"aki\Iref{3a},
A.~Mercadante\IIref{5b}{5a},
N.~Minafra\Iref{8} ,
S.~Minutoli\Iref{6a},
F.~Nemes\IAref{4}{e},
H.~Niewiadomski\Iref{8},
E.~Oliveri\Iref{7b},
F.~Oljemark\IAref{3a}{3b},
R.~Orava\IIref{3a}{3b},
M.~Oriunno\IAref{8}{f},
K.~\"{O}sterberg\IIref{3a}{3b},
P.~Palazzi\Iref{7b},
J.~Proch\'{a}zka\Iref{1a},
M.~Quinto\Iref{5a},
E.~Radermacher\Iref{8},
E.~Radicioni\Iref{5a},
F.~Ravotti\Iref{8},
E.~Robutti\Iref{6a},
L.~Ropelewski\Iref{8},
G.~Ruggiero\Iref{8},
H.~Saarikko\IIref{3a}{3b},
A.~Santroni\IIref{6b}{6a},
A.~Scribano\Iref{7b},
J.~Smajek\Iref{8},
W.~Snoeys\Iref{8},
J.~Sziklai\Iref{4},
C.~Taylor\Iref{9},
N.~Turini\Iref{7b},
V.~Vacek\Iref{1b},
M.~V\'itek\Iref{1b},
J.~Welti\IIref{3a}{3b} and
J.~Whitmore\Iref{10}
\end{Authlist}

\Instline{1a}{Institute of Physics of the Academy of Sciences of the Czech Republic, Praha, Czech Republic.}
\Instline{1b}{Czech Technical University, Praha, Czech Republic.}
\Instline{2} {National Institute of Chemical Physics and Biophysics NICPB, Tallinn, Estonia.}
\Instline{3a}{Helsinki Institute of Physics, Finland.}
\Instline{3b}{Department of Physics, University of Helsinki, Finland.}
\Instline{4} {MTA Wigner Research Center, RMKI, Budapest, Hungary.}
\Instline{5a}{INFN Sezione di Bari, Italy.}
\Instline{5b}{Dipartimento Interateneo di Fisica di Bari, Italy.}
\Instline{6a}{Sezione INFN, Genova, Italy.}
\Instline{6b}{Universit\`{a} degli Studi di Genova, Italy.}
\Instline{7a}{INFN Sezione di Pisa, Italy.}
\Instline{7b}{Universit\`{a} degli Studi di Siena and Gruppo Collegato INFN di Siena, Italy.}
\Instline{8} {CERN, Geneva, Switzerland.}
\Instline{9} {Case Western Reserve University, Dept. of Physics, Cleveland, OH, USA.}
\Instline{10}{Penn State University, Dept.~of Physics, University Park, PA, USA.}

\Anotfoot{a}{INRNE-BAS, Institute for Nuclear Research and Nuclear Energy, Bulgarian Academy of Sciences, Sofia, Bulgaria.}
\Anotfoot{b}{Ioffe Physical - Technical Institute of Russian Academy of Sciences.}
\Anotfoot{c}{Warsaw University of Technology, Poland.}
\Anotfoot{d}{Institute of Nuclear Physics, Polish Academy of Science, Cracow, Poland.}
\Anotfoot{e}{Department of Atomic Physics, E\"otv\"os University, Hungary.}
\Anotfoot{f}{SLAC National Accelerator Laboratory, Stanford CA, USA.}
\fi

%\newpage
\begin{abstract}
The TOTEM experiment at the CERN LHC has measured elastic proton-proton 
scattering at the centre-of-mass energy 
$\sqrt{s}=8\,$TeV and squared four-momentum transfers $|t|$ from $6\times10^{-4}\,\rm GeV^{2}$ to ...?
Near the lower end of the $t$-interval, for
$|t|\lesssim 2\times10^{-3}\,\rm GeV^{2}$, the differential cross-section is 
sensitive to the 
interference between the hadronic and the electromagnetic scattering amplitudes.
This article presents the measured cross-section and its interpretation for 
different assumptions on the functional form of the interference term. In 
particular, the $\rho$-parameter, i.e. the ratio between the real and the 
imaginary parts of the forward hadronic elastic amplitude, was determined.
\textbf{Give value here? For which case?}
\end{abstract}
\end{titlepage}

General note: write a (minimal but) self-contained paper, although possibly exceeding standard letter size


%--------------------------------------------------

\input introduction.tex

\input experimental_apparatus.tex

\input data_taking.tex

\input coulomb.tex

%--------------------------------------------------
\section{Discussion/Conclusions}

\> here or at the ends of sections 4 and 5 ??


%--------------------------------------------------
\section{Outlook}

\> if any...

\> what data we have and will publish in near future?


%--------------------------------------------------
\acknowledgments

\iffalse
We are indebted to the beam optics development team
%({\sc A.~Verdier} in the initial phase, {\sc H.~Burkhardt}, {\sc G.~M\" uller}, {\sc S.~Redaelli}, {\sc J.~Wenninger}, {\sc S.~M.~White})
for the design, the thorough preparations and the successful commissioning of the $\beta^* = 90\un{m}$ optics. We congratulate the CERN accelerator groups for the very smooth operation in 2011. We thank
%{\sc M.~Ferro-Luzzi}
the LHC machine coordinators for scheduling the dedicated fills.

We are grateful to CMS for providing their luminosity measurements.

This work was supported by the institutions listed on the front page and partially also by NSF (US), the Magnus
Ehrnrooth foundation (Finland), the Waldemar von Frenckell foundation (Finland), the Academy of
Finland, the OTKA grant NK 101438, 73143 (Hungary) and the NKTH-OTKA grant 74458 (Hungary).

\fi

%--------------------------------------------------
\begin{thebibliography}{99}

\bibitem{jinst}
    %The TOTEM Experiment at the CERN Large Hadron Collider, JINST 3 S08007, 2008
	\Name{Anelli G.~\etal{}~(TOTEM Collaboration)}
	\REVIEW{JINST}{3}{2008}{S08007}
\bibitem{epl95}
    %Proton-proton elastic scattering at the LHC energy of \sqrt{s} = 7 TeV, Europhys. Lett. 95 (2011) 41001,CERN-PH-EP-2011-101 
	\Name{Antchev G.~\etal{}~(TOTEM Collaboration)}
	\REVIEW{Europhys.~Lett.}{95}{2011}{41001}

\bibitem{epl96}
    %First measurements of the total proton-proton cross-section at the LHC energy of $\sqrt s =7\,\rm TeV$ CERN-PH-EP-2011-158
	\Name{Antchev G.~\etal{}~(TOTEM Collaboration)}
	\REVIEW{Europhys.~Lett.}{96}{2011}{21002}

\bibitem{epl101}
	\Name{Antchev G.~\etal{}~(TOTEM Collaboration)}
	\REVIEW{Europhys.~Lett.}{101}{2013}{21004}

\bibitem{prl111}
	\Name{Antchev G.~\etal{}~(TOTEM Collaboration)}
	\REVIEW{Phys.~Rev.~Lett.}{111}{2013}{012001}

\bibitem{kl94}
	\Name{Kundr\' at, V. and Lokaj\' i\v cek, M.}
	%title     = "High-energy scattering amplitude of unpolarized and charged hadrons",
	\REVIEW{Z.~Phys.}{C63}{1994}{619--630}
	%doi       = "10.1007/BF01557628",


\iffalse
\bibitem{P2} 
	\Name{Antchev G.~\etal{}~(TOTEM Collaboration)}
	%\REVIEW{Europhys.~Lett.}{TODO}{2012}{TODO}
	CERN-PH-EP-2012-352

\bibitem{P3} 
	\Name{Antchev G.~\etal{}~(TOTEM Collaboration)}
	%\REVIEW{Europhys.~Lett.}{TODO}{2012}{TODO}
	CERN-PH-EP-2012-353

\bibitem{jinst}
    %The TOTEM Experiment at the CERN Large Hadron Collider, JINST 3 S08007, 2008
	\Name{Anelli G.~\etal{}~(TOTEM Collaboration)}
	\REVIEW{JINST}{3}{2008}{S08007}

\bibitem{jan_thesis}
	\Name{Ka\v spar J.}
	PhD Thesis, CERN-THESIS-2011-214, {\tt http://cdsweb.cern.ch/record/1441140}

\bibitem{mario_ipac_2011}
	\Name{Deile M.}
	{\it The First 1 1/2 Years of TOTEM Roman Pot Operation at LHC}, in
	{\it Proceedings of the 2nd International Particle Accelerator Conference (IPAC 2011), San Sebastian, Spain}. 
	%{\tt http://accelconf.web.cern.ch/AccelConf/IPAC2011/papers/mopo011.pdf}
	arXiv:1110.5808v1

\bibitem{kklp}	
	\Name{Ka\v spar, J.~\etal}
	\REVIEW{Nucl.~Phys.}{B843}{2011}{84}

%\bibitem{pdg} 
%	\Name{Nakamura K.~\etal{} (Particle Data Group)}
%	\REVIEW{J.~Phys.}{G37}{2010}{075021}

\bibitem{B_vs_s}
	\Name{ISR (CR Collaboration)} \REVIEW{Phys.~Lett.}{B62}{1976}{460}; 
	\Name{ISR (ACHGT Collaboration)} \REVIEW{Phys.~Lett.}{B39}{1972}{663}; 
	\Name{ISR (R-211)} \REVIEW{Nucl.~Phys.}{B262}{1985}{689}; 
	\Name{ISR (R-210)} \REVIEW{Phys.~Lett.}{B115}{1982}{495}; 
	\Name{UA1} \REVIEW{Phys.~Lett.}{B147}{1984}{385}; 
	\Name{UA4} \REVIEW{Phys.~Lett.}{B127}{1983}{472} and \REVIEW{Phys. Lett.}{B198}{1987}{583}; 
	\Name{UA4/2} \REVIEW{Phys.~Lett.}{B316}{1993}{448}; 
	\Name{CDF} \REVIEW{Phys.~Rev.}{D50}{1994}{5518}; 
	\Name{E710} \REVIEW{Phys.~Rev.~Lett.}{68}{1992}{2433} and \REVIEW{Nuovo Cimento}{A106}{1992}{123}; 
	\Name{D0} D0 Note 6056-CONF; 
	\Name{pp2pp} \REVIEW{Phys.~Lett.}{B579}{2004}{245}

\bibitem{lafferty94}
 	% Where to stick your data points: The treatment of measurements within wide bins
	\Name{Lafferty G.~D.~and Wyatt T.~R.}
	\REVIEW{Nucl.\ Instrum.\ Meth.}{A 355}{1995}{541}

\bibitem{compete} 
	\Name{Cudell~J.~R.~\etal{} (COMPETE Collaboration)}
	\REVIEW{Phys.\ Rev.\ Lett.}{89}{2002}{201801}

\fi

\end{thebibliography}

\end{document}
