\def\DeclareAuthors{%
	\AddAuthor{G.~Antchev}{}{}{a}%
	\AddAuthor{P.~Aspell}{8}{}{}%
	\AddAuthor{I.~Atanassov}{8}{}{a}%
	\AddAuthor{V.~Avati}{8}{}{}%
	\AddAuthor{J.~Baechler}{8}{}{}%
	\AddAuthor{V.~Berardi}{5b}{5a}{}%
	\AddAuthor{M.~Berretti}{7b}{}{}%
	\AddAuthor{E.~Bossini}{7b}{}{}%
	\AddAuthor{M.~Bozzo}{6b}{6a}{}%
	\AddAuthor{P.~Brogi}{7b}{}{}%
	\AddAuthor{E.~Br\"{u}cken}{3a}{3b}{}%
	\AddAuthor{A.~Buzzo}{6a}{}{}%
	\AddAuthor{F.~S.~Cafagna}{5a}{}{}%
	\AddAuthor{M.~Calicchio}{5b}{5a}{}%
	\AddAuthor{M.~G.~Catanesi}{5a}{}{}%
	\AddAuthor{C.~Covault}{9}{}{}%
	\AddAuthor{M.~Csan\'{a}d}{4}{}{e}%
	\AddAuthor{T.~Cs\"{o}rg\H{o}}{4}{}{}%
	\AddAuthor{M.~Deile}{8}{}{}%
	\AddAuthor{K.~Eggert}{9}{}{}%
	\AddAuthor{V.~Eremin}{}{}{b}%
	\AddAuthor{R.~Ferretti}{6a}{6b}{}%
	\AddAuthor{F.~Ferro}{6a}{}{}%
	\AddAuthor{A. Fiergolski}{}{}{c}%
	\AddAuthor{F.~Garcia}{3a}{}{}%
	\AddAuthor{S.~Giani}{8}{}{}%
	\AddAuthor{V.~Greco}{7b}{8}{}%
	\AddAuthor{L.~Grzanka}{8}{}{d}%
	\AddAuthor{J.~Heino}{3a}{}{}%
	\AddAuthor{T.~Hilden}{3a}{3b}{}%
	\AddAuthor{R.~A.~Intonti}{5a}{}{}%
	\AddAuthor{J.~Ka\v{s}par}{1a}{8}{}%
	\AddAuthor{J.~Kopal}{1a}{8}{}%
	\AddAuthor{V.~Kundr\'{a}t}{1a}{}{}%
	\AddAuthor{K.~Kurvinen}{3a}{}{}%
	\AddAuthor{S.~Lami}{7a}{}{}%
	\AddAuthor{G.~Latino}{7b}{}{}%
	\AddAuthor{R.~Lauhakangas}{3a}{}{}%
	\AddAuthor{T.~Leszko}{}{}{c}%
	\AddAuthor{E.~Lippmaa}{2}{}{}%
	\AddAuthor{M.~Lokaj\'{\i}\v{c}ek}{1a}{}{}%
	\AddAuthor{M.~Lo~Vetere}{6b}{6a}{}%
	\AddAuthor{F.~Lucas~Rodr\'{i}guez}{8}{}{}%
	\AddAuthor{M.~Macr\'{\i}}{6a}{}{}%
	\AddAuthor{T.~M\"aki}{3a}{}{}%
	\AddAuthor{A.~Mercadante}{5b}{5a}{}%
	\AddAuthor{N.~Minafra}{8}{}{} %
	\AddAuthor{S.~Minutoli}{6a}{}{}%
	\AddAuthor{F.~Nemes}{4}{}{e}%
	\AddAuthor{H.~Niewiadomski}{8}{}{}%
	\AddAuthor{E.~Oliveri}{7b}{}{}%
	\AddAuthor{F.~Oljemark}{3a}{3b}{}%
	\AddAuthor{R.~Orava}{3a}{3b}{}%
	\AddAuthor{M.~Oriunno}{8}{}{f}%
	\AddAuthor{K.~\"{O}sterberg}{3a}{3b}{}%
	\AddAuthor{P.~Palazzi}{7b}{}{}%
	\AddAuthor{J.~Proch\'{a}zka}{1a}{}{}%
	\AddAuthor{M.~Quinto}{5a}{}{}%
	\AddAuthor{E.~Radermacher}{8}{}{}%
	\AddAuthor{E.~Radicioni}{5a}{}{}%
	\AddAuthor{F.~Ravotti}{8}{}{}%
	\AddAuthor{E.~Robutti}{6a}{}{}%
	\AddAuthor{L.~Ropelewski}{8}{}{}%
	\AddAuthor{G.~Ruggiero}{8}{}{}%
	\AddAuthor{H.~Saarikko}{3a}{3b}{}%
	\AddAuthor{A.~Santroni}{6b}{6a}{}%
	\AddAuthor{A.~Scribano}{7b}{}{}%
	\AddAuthor{J.~Smajek}{8}{}{}%
	\AddAuthor{W.~Snoeys}{8}{}{}%
	\AddAuthor{J.~Sziklai}{4}{}{}%
	\AddAuthor{C.~Taylor}{9}{}{}%
	\AddAuthor{N.~Turini}{7b}{}{}%
	\AddAuthor{V.~Vacek}{1b}{}{}%
	\AddAuthor{M.~V\'itek}{1b}{}{}%
	\AddAuthor{J.~Welti}{3a}{3b}{}%
	\AddAuthor{J.~Whitmore}{10}{}{}%
}

%----------------------------------------------------------------------------------------------------

\def\DeclareInstitutes{%
	\AddInstitute{1a}{Institute of Physics of the Academy of Sciences of the Czech Republic, Praha, Czech Republic.}
	\AddInstitute{1b}{Czech Technical University, Praha, Czech Republic.}
	\AddInstitute{2} {National Institute of Chemical Physics and Biophysics NICPB, Tallinn, Estonia.}
	\AddInstitute{3a}{Helsinki Institute of Physics, Finland.}
	\AddInstitute{3b}{Department of Physics, University of Helsinki, Finland.}
	\AddInstitute{4} {MTA Wigner Research Center, RMKI, Budapest, Hungary.}
	\AddInstitute{5a}{INFN Sezione di Bari, Italy.}
	\AddInstitute{5b}{Dipartimento Interateneo di Fisica di Bari, Italy.}
	\AddInstitute{6a}{Sezione INFN, Genova, Italy.}
	\AddInstitute{6b}{Universit\`{a} degli Studi di Genova, Italy.}
	\AddInstitute{7a}{INFN Sezione di Pisa, Italy.}
	\AddInstitute{7b}{Universit\`{a} degli Studi di Siena and Gruppo Collegato INFN di Siena, Italy.}
	\AddInstitute{8} {CERN, Geneva, Switzerland.}
	\AddInstitute{9} {Case Western Reserve University, Dept. of Physics, Cleveland, OH, USA.}
	\AddInstitute{10}{Penn State University, Dept.~of Physics, University Park, PA, USA.}
}

%----------------------------------------------------------------------------------------------------
	
\def\DeclareExternalInstitutes{%
	\AddExternalInstitute{a}{INRNE-BAS, Institute for Nuclear Research and Nuclear Energy, Bulgarian Academy of Sciences, Sofia, Bulgaria.}
	\AddExternalInstitute{b}{Ioffe Physical - Technical Institute of Russian Academy of Sciences.}
	\AddExternalInstitute{c}{Warsaw University of Technology, Poland.}
	\AddExternalInstitute{d}{Institute of Nuclear Physics, Polish Academy of Science, Cracow, Poland.}
	\AddExternalInstitute{e}{Department of Atomic Physics, E\"otv\"os University, Hungary.}
	\AddExternalInstitute{f}{SLAC National Accelerator Laboratory, Stanford CA, USA.}
}
