\documentclass[pdftex,twocolumn,epjc3]{svjour3}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{mathptmx}

%----------------------------------------------------------------------------------------------------

\def\d{{\rm d}}
\def\un#1{\,{\rm #1}}
\def\ung#1{\quad[{\rm #1}]}
\def\unt#1{[{\rm #1}]}
\def\e{{\rm e}}
\def\I{{\rm i}}
\def\T{{\rm T}}
%\def\vec#1{\mathbf{#1}}
\def\vec#1{#1} % TODO
\def\mat#1{\mathsf{#1}}
\def\etal{et al.}
\def\todo#1{{\color{red} #1}}

\setbox123\hbox{$0$}
\setbox124\hbox{$.$}
\def\S{\hbox to\wd123{\hss}}
\def\.{\hbox to\wd124{\hss}}

% TODO: needed?
\bgroup
\catcode`\@=11

\gdef\thanksRef#1#2{%
    \protected@xdef\@thanks{\@thanks\protect\footnotetext[#1]{#2}}%
}
\egroup

% TODO: needed?
\def\hang{\hangindent=\parindent}
\catcode`\>=11
\newskip\itskip \itskip2mm
\newskip\iitskip \iitskip0mm
\newdimen\itindent \itindent3mm
\newdimen\iitindent \iitindent5mm
\def\>{\par\vskip\itskip\parindent\itindent\indent\hang\llap{\hbox to3mm{$\bullet$\hss}}}
\def\>E{\par\vskip\itskip\parindent\itindent\indent\hang\llap{\hbox to3mm{\hss}}}
\def\>>{\par\vskip\iitskip\parindent\iitindent\indent\hang\llap{\hbox to\iitindent{\hss--\ }}}

\def\Name#1{\textsc{#1}, }
\def\REVIEW#1#2#3#4{{\it #1} {\bf #2} (#3) #4}

%----------------------------------------------------------------------------------------------------

\journalname{Eur. Phys. J. C}

\begin{document}

\title{Evidence for non-exponential elastic differential cross-section at low $|\hbox{t}|$ and $\sqrt{\hbox{s}}$ = 8 TeV} % with TOTEM ?

\authorrunning{Short form of author}
\titlerunning{Short form of title}

\input authorlist_epjc

\date{\today}

\maketitle

\begin{abstract}
The TOTEM experiment has made a high-precision measurement of the elastic 
proton-proton differential cross-section at the centre-of-mass energy 
$\sqrt s = 8\un{TeV}$ based on a new high-statistics data sample obtained with 
the $\beta^* = 90\un{m}$ optics. 
%Furthermore, thanks to an improved analysis procedure, an unprecedented precision has been reached: 
Both statistical and systematic uncertainties remain below $1\un{\%}$, except 
the contribution from the overall normalisation which was obtained from 
another data set. This unprecedented precision allows to exclude a purely exponential cross-section in the range of four-momentum transfer squared $0.027 < |t| < 0.2\un{GeV^2}$ with a significance greater than $7\un{\sigma}$. Consequently, the extrapolation to $t=0$ is reviewed and two extended models are presented, yielding total cross-section estimates $(100.8 \pm 2.1)\un{mb}$ and $(101.2 \pm 2.1)\un{mb}$, well compatible with previous TOTEM measurements.
%
%Analysis of a new dataset obtained at $\sqrt{s} = 8\un{TeV}$ and $\beta^* = 90\un{m}$ optics.
%High statistics (more than $7\cdot10^{6}$ elastic events)
%$\Rightarrow$ strongly reduced statistical and systematic uncertainties (each below $1\un{\%}$) % excluding normalisation unc.
%$\Rightarrow$ purely exponential behaviour of differential cross-section excluded at more than $7\un{\sigma}$ significance
%$\Rightarrow$ new determination of the total cross-section (non-exponential extrapolation), values, but still compatible with the previous TOTEM measurements.

\keywords{elastic scattering \and total cross-section \and LHC}
\PACS{13.60.Hb} % Total and inclusive cross sections (including deep-inelastic processes)
%\preprint{CERN-PH-EP-2014-XXXX}

\end{abstract}

%--------------------------------------------------

\input introduction

\input experimental_apparatus

\input data_taking

\input differential_cross_section

%--------------------------------------------------

\iffalse
\section{Conclusions}

new data - high statistics
new analysis - only irreducible unc. left - which ones
unprecedented precision in a range
data exclude pure exponential in that range, two methods, 7sigma
extended models for extrapolation to t=0, sigma\_tot compatible to previous TOTEM measurement
\fi

%--------------------------------------------------

\begin{acknowledgements}
THIS IS JUST PLACEHOLDER -----------
We are indebted to the beam optics development team
for the design, the thorough preparations and the successful commissioning of the $\beta^* = 90\un{m}$ optics. We congratulate the CERN accelerator groups for the very smooth operation in 2011. We thank
the LHC machine coordinators for scheduling the dedicated fills.

This work was supported by the institutions listed on the front page and partially also by NSF (US), the Magnus
Ehrnrooth foundation (Finland), the Waldemar von Frenckell foundation (Finland), the Academy of
Finland, the OTKA grant NK 101438, 73143 (Hungary) and the NKTH-OTKA grant 74458 (Hungary).
----------- END OF THE PLACEHOLDER
\end{acknowledgements}


%----------------------------------------------------------------------------------------------------
\begin{thebibliography}{99}
%
\bibitem{plb39} \Name{G. Barbiellini et al.} \REVIEW{Phys.~Lett.}{B39}{1972}{663}.
\bibitem{plb115} \Name{M. Ambrosio et al.} \REVIEW{Phys.~Lett.}{B115}{1982}{495}.
\bibitem{npb141} \Name{L. Baksay et al.} \REVIEW{Nucl.~Phys.}{B141}{1978}{1}.
\bibitem{npb248} \Name{A. Breakstone et al.} \REVIEW{Nucl.~Phys.}{B248}{1984}{253}.
\bibitem{plb147} \Name{M. Bozzo et al.} \REVIEW{Phys.~Lett.}{B147}{1984}{385}; 
\bibitem{epl96}
    %First measurements of the total proton-proton cross-section at the LHC energy of $\sqrt s =7\,\rm TeV$ CERN-PH-EP-2011-158
	\Name{Antchev G.~\etal{}~(TOTEM Collaboration)}
	\REVIEW{Europhys.~Lett.}{96}{2011}{21002}
\bibitem{epl101-el}
	\Name{Antchev G.~\etal{}~(TOTEM Collaboration)}
	\REVIEW{Europhys.~Lett.}{101}{2013}{21002}


\bibitem{prl111} 
	\Name{G. Antchev~\etal{}~(TOTEM Collaboration)}
	\REVIEW{Phys.~Rev.~Lett.}{111}{2013}{012001}

\bibitem{alfa} \Name{The ATLAS Collaboration} ATLAS-CONF-2014-040.

\bibitem{totem-jinst}
    %The TOTEM Experiment at the CERN Large Hadron Collider, JINST 3 S08007, 2008
	\Name{Anelli G.~\etal{}~(TOTEM Collaboration)}
	\REVIEW{JINST}{3}{2008}{S08007}


\bibitem{totem-ijmp}
	% Performance of the Totem Detectors at the LHC
	\Name{Antchev G.~\etal{}~(TOTEM Collaboration)}
	\REVIEW{Int.~J.~Mod.~Phys.~A}{28}{2013}{1330046}

\bibitem{totem-optics}
	\Name{Antchev G.~\etal{}~(TOTEM Collaboration)}
	LHC Optics Measurement with Proton Tracks Detected by the Roman Pots of the TOTEM Experiment, 
	arXiv:1406.0546

\bibitem{compete} 
	\Name{Cudell~J.~R.~\etal{} (COMPETE Collaboration)}
	\REVIEW{Phys.\ Rev.\ Lett.}{89}{2002}{201801}

\bibitem{lafferty94}
 	% Where to stick your data points: The treatment of measurements within wide bins
	\Name{Lafferty G.~D.~and Wyatt T.~R.}
	\REVIEW{Nucl.\ Instrum.\ Meth.}{A 355}{1995}{541}


\iffalse

\bibitem{epl95}
    %Proton-proton elastic scattering at the LHC energy of \sqrt{s} = 7 TeV, Europhys. Lett. 95 (2011) 41001,CERN-PH-EP-2011-101 
	\Name{Antchev G.~\etal{}~(TOTEM Collaboration)}
	\REVIEW{Europhys.~Lett.}{95}{2011}{41001}


\bibitem{epl101-inel}
	\Name{Antchev G.~\etal{}~(TOTEM Collaboration)}
	\REVIEW{Europhys.~Lett.}{101}{2013}{21003}

\bibitem{epl101-tot}
	\Name{Antchev G.~\etal{}~(TOTEM Collaboration)}
	\REVIEW{Europhys.~Lett.}{101}{2013}{21004}

\bibitem{jan_thesis}
	\Name{Ka\v spar J.}
	PhD Thesis, CERN-THESIS-2011-214, {\tt http://cdsweb.cern.ch/record/1441140}

\bibitem{mario_ipac_2011}
	\Name{Deile M.}
	{\it The First 1 1/2 Years of TOTEM Roman Pot Operation at LHC}, in
	{\it Proceedings of the 2nd International Particle Accelerator Conference (IPAC 2011), San Sebastian, Spain}. 
	%{\tt http://accelconf.web.cern.ch/AccelConf/IPAC2011/papers/mopo011.pdf}
	arXiv:1110.5808v1

%\bibitem{pdg} 
%	\Name{Nakamura K.~\etal{} (Particle Data Group)}
%	\REVIEW{J.~Phys.}{G37}{2010}{075021}

%\bibitem{B_vs_s}
%	\Name{ISR (CR Collaboration)} \REVIEW{Phys.~Lett.}{B62}{1976}{460}; 
%	\Name{ISR (ACHGT Collaboration)} \REVIEW{Phys.~Lett.}{B39}{1972}{663}; 
%	\Name{ISR (R-211)} \REVIEW{Nucl.~Phys.}{B262}{1985}{689}; 
%	\Name{ISR (R-210)} \REVIEW{Phys.~Lett.}{B115}{1982}{495}; 
%	\Name{UA4} \REVIEW{Phys.~Lett.}{B147}{1984}{385}; 
%	\Name{UA4} \REVIEW{Phys.~Lett.}{B127}{1983}{472} and \REVIEW{Phys. Lett.}{B198}{1987}{583}; 
%	\Name{UA4/2} \REVIEW{Phys.~Lett.}{B316}{1993}{448}; 
%	\Name{CDF} \REVIEW{Phys.~Rev.}{D50}{1994}{5518}; 
%	\Name{E710} \REVIEW{Phys.~Rev.~Lett.}{68}{1992}{2433} and \REVIEW{Nuovo Cimento}{A106}{1992}{123}; 
%	\Name{D0} D0 Note 6056-CONF; 
%	\Name{pp2pp} \REVIEW{Phys.~Lett.}{B579}{2004}{245}

\fi

\end{thebibliography}



\end{document}
