\def\yes{yes}

\input utf8-csf

\ifx\InSummary\yes
\else
	\input base
	\input article

	\centerline{\bf List of Publications by Jan Ka\v spar}
	\vskip2\baselineskip
\fi

\itskip5pt

\noindent Selected publications of the TOTEM experiment (I am a coauthor of more than 20 publications)

\> ANTCHEV, G. et al. (TOTEM collaboration). {\it First measurement of the total proton-proton cross-section at the LHC energy of $\sqrt s = 7\,TeV$}. Europhys. Lett. 96 (2011) 21002.

\> ANTCHEV, G. et al. (TOTEM collaboration). {\it Proton-proton elastic scattering at the LHC energy of $\sqrt s = 7\,TeV$}. Europhys. Lett. 95 (2011) 41001.

\> KAŠPAR, J. (TOTEM collaboration). {\it TOTEM Experiment: Elastic and Total Cross Sections}. Presented at 13th International Conference on Elastic and Diffractive Scattering, CERN, Geneva, Switzerland, 29th June - 3rd July 2009. E-print: arXiv:1002.3527.

\> KAŠPAR, J. (TOTEM collaboration). {\it First results of the TOTEM Roman Pots}. Presented at Vertex 2010: 19th International Workshop on Vertex Detectors, Loch Lomond, Glasgow, Scotland, United Kingdom, 6-11 Jun 2010. Published in PoS.

\> KAŠPAR, J. (TOTEM collaboration). {\it Soft physics at the LHC with TOTEM}. Presented at 23th Les Rencontres de Physique de La Vallee d'Aoste, La Thuile, Aosta Valley, Italy, 1-7 Mar 2009. Published in Nuovo Cim. C32 (2009) 105-112.

\> ANELLI, G. et al. (TOTEM collaboration). {\it The TOTEM experiment at the CERN Large Hadron Collider}. JINST 3 (2008).


\vskip2\baselineskip
\noindent Other publications

%------ Kundrát et al. -------

\> KAŠPAR, J., KUNDRÁT, V., LOKAJÍČEK, M. and PROCHÁZKA, J. {\it Phenomenological models of elastic nucleon scattering and predictions for LHC}. Nucl. Phys. B843 (2011) 84-106.

\> KUNDRÁT, V., LOKAJÍČEK, M., KAŠPAR, J. and PROCHÁZKA, J. {\it Problems of phenomenological description of elastic pp scattering at the LHC: Predictions of contemporary models}. Presented at Physics at LHC, La Biodola, Isola d'Elba, Italy, 27-29 May 2010. Published in La Biodola 2010, Forward physics at the LHC 26-35.

\> KAŠPAR, J., KUNDRÁT, V. and LOKAJÍČEK, M. {\it Contemporary models of elastic nucleon scattering and their predictions for LHC}. E-print: arXiv:0912.0112 (2009).

\> KUNDRÁT, V., KAŠPAR, J. and LOKAJÍČEK, M. {\it Theoretical aspects of high energy elastic nucleon scattering}. E-print: arXiv:0912.1188 (2009).

\> KUNDRÁT, V., KAŠPAR, J. and LOKAJÍČEK, M. {\it To the theory of high-energy elastic nucleon collisions}. E-print: arXiv:0712.1503 (2007).

\> KUNDRÁT, V., KAŠPAR, J. and LOKAJÍČEK, M. {\it To the theory of high-energy elastic nucleon collisions}. Presented at 12th International Conference on Elastic and diffractive scattering, Hamburg, Germany, May 21-25, 2007. E-print: arXiv:0712.3633.

%------- ISLAM -------

\> ISLAM, M. M., KAŠPAR, J. and LUDDY, R. J. {\it Deep-elastic pp scattering at LHC from low-x gluons}. Mod. Phys. Lett. A24 (2009) 485-496.

\> ISLAM, M. M., LUDDY, R. J., KAŠPAR, J. and PROKUDIN, A. {\it Picturing the proton by elastic scattering}. CERN Cour. 49 (2009) 35-37.
	
\> ISLAM, M. M., KAŠPAR, J. and LUDDY, R. J. {\it Proton-Proton Elastic Scattering at LHC and Proton Structure}. Presented at 13th International Conference on Elastic and Diffractive Scattering, CERN, Geneva, Switzerland, 29 Jun - 03 Jul 2009.

\> ISLAM, M. M., KAŠPAR, J. and LUDDY, R. J. {\it pp Elastic Scattering at LHC in a Nucleon-Structure Model}. Presented at 12th International Conference on Elastic and Diffractive Scattering, Hamburg, DESY, Germany, 21-25 May 2007.

\bye
